\documentstyle[amiga,12pt,a4]{article}

\begin{document}

\advance \textwidth by -2em
\parindent -2em

\centerline{\Huge\bf Who's On First}
\centerline{\large\sl (Sketch by Bud Abbot and Lou Costello)}
\vspace{1.8cm}

{\bf Lou:} I love baseball.  When we get to St.  Louis, will you tell me
the guys' name on the team so when I go to see them in that St.  Louis ball
park I'll be able to know those fellows?

{\bf Bud:} All right.  but you know, strange as it may seems, they give
ball players nowadays very peculiar names, nick names, like ``Dizzy Dean.''
Now on the St.  Louis team we have Who's on first, What's on second, I
Don't Know is on third ---

{\bf Lou:} That's what I want to find out.  I want you to tell me the names
of the fellows on the St.  Louis team.

{\bf Bud:} I'm telling you.  Who's on first, What's on second, I Don't Know
is on third ---

{\bf Lou:}   You know the fellows' names?

{\bf Bud:}   Yes.

{\bf Lou:}   Well, then who's playin' first.

{\bf Bud:}   Yes

{\bf Lou:}   I mean the fellow's name on first base.

{\bf Bud:}   Who.

{\bf Lou:}   The fellow playin' first base for St. Louis.

{\bf Bud:}   Who.

{\bf Lou:}   The guy on first base.

{\bf Bud:}   Who is on first.

{\bf Lou:}   Well, what are you askin' me for?

{\bf Bud:}   I'm not asking you --- I'm telling you.  WHO IS ON FIRST.

{\bf Lou:}   I'm asking you --- who's on first?

{\bf Bud:}   That's the man's name!

{\bf Lou:}   That's who's name?

{\bf Bud:}   Yes.

{\bf Lou:}   Well, go ahead and tell me.

{\bf Bud:}   Who.

{\bf Lou:}   The guy on first.

{\bf Bud:}   Who.

{\bf Lou:}   The first baseman.

{\bf Bud:}   Who is on first.

{\bf Lou:}   Have you got a first baseman on first?

{\bf Bud:}   Certainly.

{\bf Lou:}   Then who's playing first?

{\bf Bud:}   Absolutely.

{\bf Lou:} {\sl(pause)} When you pay off the first baseman every month, who gets
the money?

{\bf Bud:}   Every dollar of it.  And why not, the man's entitled to it.

{\bf Lou:}   Who is?

{\bf Bud:}   Yes.

{\bf Lou:}   So who gets it?

{\bf Bud:} Why shouldn't he?  Sometimes his wife comes down and collects
it.

{\bf Lou:}   Who's wife?

{\bf Bud:}   Yes.  After all the man earns it.

{\bf Lou:}   Who does?

{\bf Bud:}   Absolutely.

{\bf Lou:} Well all I'm trying to find out is what's the guys name on first
base.

{\bf Bud:}   Oh, no, no, What is on second base.

{\bf Lou:}   I'm not asking you who's on second.

{\bf Bud:}   Who's on first.

{\bf Lou:}   That's what I'm trying to find out.

{\bf Bud:}   Well, don't change the players around.

{\bf Lou:}   I'm not changing nobody.

{\bf Bud:}   Now, take it easy.

{\bf Lou:}   What's the guy's name on first base?

{\bf Bud:}   What's the guy's name on second base.

{\bf Lou:}   I'm not askin' ya who's on second.

{\bf Bud:}   Who's on first.

{\bf Lou:}   I don't know.

{\bf Bud:}   He's on third.  We're not talking about him.

{\bf Lou:}   How could I get on third base?

{\bf Bud:}   You mentioned his name.

{\bf Lou:} If I mentioned the third baseman's name, who did I say is
playing third?

{\bf Bud:}   No, Who's playing first.

{\bf Lou:}   Stay offa first, will ya?

{\bf Bud:}   Well what do you want me to do?

{\bf Lou:}   Now what's the guy's name on first base?

{\bf Bud:}   What's on second.

{\bf Lou:}   I'm not asking ya who's on second.

{\bf Bud:}   Who's on first.

{\bf Lou:}   I don't know.

{\bf Bud:}   He's on third.

{\bf Lou:}   There I go back on third again.

{\bf Bud:}   Well, I can't change their names.

{\bf Lou:}   Say, will you please stay on third base.

{\bf Bud:}   Please.  Now what is it you want to know.

{\bf Lou:}   What is the fellow's name on third base.

{\bf Bud:}   What is the fellow's name on second base.

{\bf Lou:}   I'm not askin' ya who's on second.

{\bf Bud:}   Who's on first.

{\bf Lou:}   I don't know.

{\bf Bud:}   THIRD BASE!

{\bf Lou:}   You got an outfield?

{\bf Bud:}   Oh, sure.

{\bf Lou:}   St. Louis has got a good outfield?

{\bf Bud:}   Oh, absolutely.

{\bf Lou:}   The left fielder's name?

{\bf Bud:}   Why.

{\bf Lou:}   I don't know, I just thought I'd ask.

{\bf Bud:}   Well, I just thought I'd tell you.

{\bf Lou:}   Them tell me who's playing left field.

{\bf Bud:}   Who's playing first.

{\bf Lou:}   Stay out of the infield!

{\bf Bud:}   Don't mention any names out here.

{\bf Lou:}   I want to know what's the fellow's name on left field?

{\bf Bud:}   What is on second.

{\bf Lou:}   I'm not askin' ya who's on second.

{\bf Bud:}   Who is on first.

{\bf Lou:}   I don't know.

{\bf Bud \& Lou:} {\sl (together and calmly)} Third base.

{\bf Lou:}   And the left fielder's name?

{\bf Bud:}   Why.

{\bf Lou:}   Because.

{\bf Bud:}   Oh he's Center Field.

{\bf Lou:}   {\sl (whimpers)} Center field.

{\bf Bud:}   Yes.

{\bf Lou:}   Wait a minute.  You got a pitcher on this team.

{\bf Bud:}   Wouldn't this be a fine team without a pitcher.

{\bf Lou:}   I don't know.  Tell me the pitcher's name.

{\bf Bud:}   Tomorrow.

{\bf Lou:}   You don't want to tell me today?

{\bf Bud:}   I'm tell you, man.

{\bf Lou:}   Then go ahead.

{\bf Bud:}   Tomorrow.

{\bf Lou:}   What time?

{\bf Bud:}   What time what?

{\bf Lou:}   What time tomorrow are you gonna tell me who's pitching?

{\bf Bud:}   Now listen, Who is not pitching.  Who is on ---

{\bf Lou:}   I'LL BREAK YOU ARM IF YOU SAY ``WHO'S ON FIRST!''

{\bf Bud:}   Then why come up here and ask?

{\bf Lou:}   I want to know what's the pitcher's name.

{\bf Bud:}   What's on second.

{\bf Lou:}   I don't know.

{\bf Bud \& Lou:} {\sl (very quickly)} THIRD BASE!!

{\bf Lou:}   You gotta Catcher?

{\bf Bud:}   Yes.

{\bf Lou:}   The Catcher's name?

{\bf Bud:}   Today.

{\bf Lou:}   Today.  And Tomorrow's pitching.

{\bf Bud:}   Now you've got it.

{\bf Lou:}   That's all.  St. Louis hat a couple of days on their team.

{\bf Bud:}   Well I can't help that.

{\bf Lou:}   You know I'm a good catcher too.

{\bf Bud:}   I know that.

{\bf Lou:}   I would like to play for the St. Louis team.

{\bf Bud:}   Well I might arrange that.

{\bf Lou:} I would like to catch.  Now I'm being a good Catcher, tomorrow's
pitching on the team, and I'm catching.

{\bf Bud:}   Yes.

{\bf Lou:}   Tomorrow throws the ball and the guy up bunts the ball.

{\bf Bud:}   Yes.

{\bf Lou:} Now when he bunts the ball --- me being a good catcher --- I
want to throw the guy out a first base, so I pick up the ball and throw it
to who?

{\bf Bud:}   Now that's the first thing you've said right.

{\bf Lou:}   I DON'T EVEN KNOW WHAT I'M TALKING ABOUT!!!!!

{\bf Bud:}   Well, that's all you have to do.

{\bf Lou:}   Is to throw it to first base.

{\bf Bud:}   Yes.

{\bf Lou:}   Now who's got it?

{\bf Bud:}   Naturally.

{\bf Lou:}   Who has it?

{\bf Bud:}   Naturally.

{\bf Lou:}   Naturally.

{\bf Bud:}   Naturally.

{\bf Lou:}   O.K.

{\bf Bud:}   Now you've got it.

{\bf Lou:}   I pick up the ball and I throw it to Naturally.

{\bf Bud:}   No you don't. You throw the ball to first base.

{\bf Lou:}   Then who gets it?

{\bf Bud:}   Naturally.

{\bf Lou:}   O.K.

{\bf Bud:}   All right.

{\bf Lou:}   I throw the ball to Naturally.

{\bf Bud:}   You don't you throw it to Naturally.

{\bf Lou:}   Naturally.

{\bf Bud:}   Well, naturally.  Say it that way.

{\bf Lou:}   That's what I said.

{\bf Bud:}   You did not.

{\bf Lou:}   I said I'd throw the ball to Naturally.

{\bf Bud:}   You don't.  You throw it to Who.

{\bf Lou:}   Naturally.

{\bf Bud:}   Yes.

{\bf Lou:}   So I throw the ball to first base and Naturally gets it.

{\bf Bud:}   No.  You throw the ball to first base---

{\bf Lou:}   Then who gets it?

{\bf Bud:}   Naturally.

{\bf Lou:}   That's what I'm saying.

{\bf Bud:}   You're not saying that.

{\bf Lou:}   I throw the ball to Naturally.

{\bf Bud:}   You throw it to Who!

{\bf Lou:}   Naturally.

{\bf Bud:}   Naturally.  Well say it that way.

{\bf Lou:}   THAT'S WHAT I'M SAYING!

{\bf Bud:}   Now don't get excited.

{\bf Lou:}   Whose gettin excited!!  I throw the ball to first base---

{\bf Bud:}   Then Who gets it.

{\bf Lou:} {\sl (annoyed)} HE BETTER GET IT!

{\bf Bud:}   That's it.  All right now Take it easy.

{\bf Lou:}   Hrmmph.

{\bf Bud:}   Hrmmph.

{\bf Lou:} Now I throw the ball to first base, whoever it is grabs the
ball, so the guy runs to second.

{\bf Bud:}   Uh-huh.

{\bf Lou:} Who picks up the ball and throws it to what.  What throws it to
I don't know.  I don't know throws it back to tomorrow --- a triple play.

{\bf Bud:}   Yeah.  It could be.

{\bf Lou:} Another guy gets up and it's a long fly ball to center.  Why?  I
don't know, he's on third, and I don't give a darn.

{\bf Bud:}   What did you say.

{\bf Lou:}   I said ``I don't give a darn.''

{\bf Bud:}   Oh, that's our shortstop!

{\bf Lou:}   ABBOTT!

\end{document}