From Martin_Steppler@mowgli.fido.de Thu Jul  9 00:13:58 1992
Received: from urmel.informatik.rwth-aachen.de ([137.226.112.21]) by toadflax.cs.ucdavis.edu (4.1/UCD.CS.2.0)
	id AA03592; Thu, 9 Jul 92 00:13:42 PDT
Received: from dfv.rwth-aachen.de (zruty.dfv.rwth-aachen.de) by urmel.informatik.rwth-aachen.de (4.1/urmel-MX.31)
	id AA24290; Thu, 9 Jul 92 09:14:03 +0200
Received: by dfv.rwth-aachen.de (4.1/dfvr.2.0)
	id AA23039; Wed, 8 Jul 92 21:05:58 +0200
Received: by sungate.fido.de (4.1/mj-1.6)
	id AA17958; Wed, 8 Jul 92 01:35:06 +0200
Received: by p1.hippo.fido.de (funpack 2.3-2.40)
	id AA17948; Wed,  8 Jul 92 01:35:02 +0200 (MET DST)
Date: Tue,  7 Jul 92 21:52:12 +0200
From: Martin_Steppler@mowgli.fido.de (Martin Steppler)
Subject: TeXt Plus Prof. 4.00 available per ftp
Message-Id: <11BF@p12.f7.n242.z2.fidonet.org>
To: announce@cs.ucdavis.edu (Dan Zerkle)
Lines: 55
Status: R

Hi Dan,

I hope this time neither the content of the posting nor several earthquakes
will prevent you from posting the following to c.s.a.a.

CU and don't stay busy ;-)

        Martin

----------cut-here--------------------------------------------------------
NAME                    TeXt Plus Professional V4.00

DESCRIPTION             TeXt  Plus  Professional  is  a TeX frontend word-
                        processor, i. e. with the help of TPP you are able
                        to create TeX-documents  without  having  to  know
                        anything  about  TeX. TPP makes use of PasTeX, the
                        Amiga  implementation  of  TeX  written  by  Georg
                        Hessmann.  New  features  are:  tables,  staggered
                        lists, mailmerge,  footnotes,  insertion  of  iff-
                        graphics  into  the  text, an ARexx-port with more
                        than  100  commands,  online  help,  full  OS  2.0
                        compatibility. You can access all features of  TeX
                        even  if  they  are not directly supported by TPP,
                        e.g. there is no editor for mathematical formulae,
                        yet, but you can insert them in  TeX-style.  Three
                        types  of documents are supported: letter, article
                        and  book.  Beautiful  letters   and    scientific
                        publications  can now be published in a minimum of
                        time    and    effort.   TPP  combines  its  user-
                        friendliness with the  typesetting-power  of  TeX.
                        TPP  V4.00 is available in both German and English
                        version and is shareware.

HARD- AND SOFTWARE-     - Amiga OS 2.04
REQUIREMENTS            - at least 2 MB RAM
                        - at least 10 MB harddisk space
                        - PasTeX V1.3 (incl. NICETeX)

DOWNLOAD                TPP400N.lha  (426196 bytes, German version)
                        TPP400EN.lha (408098 bytes, English version)

                        FTP:

                        amiga.physik.unizh.ch [130.60.80.80]

                        FIDO:
                            Mowgli 2:242/7 +49-(0)241-40 59 49

                        PasTeX:
                            ftp.uni-passau.de
                                /pub/amiga/tex/PasTeX13

AUTHOR                  Martin Steppler
                        Internet: steppler@pool.informatik.rwth-aachen.de
                        Fido:     2:242/7.12

